Rapid cycleway prioritisation tool

### 2020-06-04 code/index.Rmd
Revert to original index

The [rapid cycleway prioritisation tool](https://www.cyipt.bike/rapid/) helps identify road sections for road space reallocation and other interventions to create new cycleways.
Used with local knowledge, it provides a strong evidence base to support planning of rapid measures to support safe travel as part of the COVID-19 response.
In the context of COVID-19, big decisions need to be made **rapidly**.

>>>>

The [rapid cycleway prioritisation tool](https://www.cyipt.bike/rapid/) helps identifys road sections for road space reallocation and other interventions to create new cycleways.
Used with local knowledge, it provides a strong evidence base to support planning of rapid measures to support safe travel as part of the COVID-19 response.
In the context of COVID-19, big decisions need to be made **rapidly**.
